Rising from the Ashes II: Did the Birth of the Milky Way's Bar Give Birth to the Birth of the Abundance Bimodality

### 2024-09-07 paper/ms.tex
Add zoomed evol hist plot

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{fig/392276_SFH_AGN_M200_zoomed.pdf}
  \caption{\textbf{At the transition from the high- to low-$\alpha$ sequence, a bar forms and strengthens, AGN activity is enhanced, and star formation is supressed.} The evolutionary history of our SoI near the transition between the high- and low-$\alpha$ sequence, which is indicated as a vertical dashed line at an age of $10.6\,\Gyr$ ($t\sim3.2\,\Gyr$). The blue line indicates the SFR, which drops from a peak of $\sim54\,\Msunyr$ to $\sim3.6\,\Msunyr$. The minimum is very close to the transition. The drop in SFR is coincident with a rise in the AGN accretion rate (orange) as well as a rise in the strength of the bar (red).}
  \label{fig:history_zoom}
\end{figure}

We show the evolution of the SoI in greater detail at the transition between the high- and low-$\alpha$ sequences in Figure~\ref{fig:history_zoom}. As in Figure~\ref{fig:history} we indicate the SFR (blue) and black hole accretion rate (orange), but we also include the strength of the bar, taken to be the maximum value of $A_2$, in red. From $\sim2.8\,\Gyr$ to $\sim3.2\,\Gyr$, the SFR drops from $\sim54\,\Msunyr$ to $3.6\,\Gyr$. The minimum in the SFR is nearly coincident with the transition line.

We can see more clearly here that the BH accretion rate (red), in units of the Eddington accretion rate, increases from a value of $\sim0.08$ at $\sim2.8\,\Gyr$ to a maximum of $\sim0.3$ at $\sim3.1\,\Gyr$, right before the transition. This rise in the AGN accretion rate is preceded by a strengthening of the bar, which rises from an $A_2$ of $\sim0.1$ at $t\sim2.4\,\Gyr$ to an $A_2$ of $\sim0.5$ at $\sim3.1\,\Gyr$, the time of the peak BH accretion rate.
